Survivable Set Connectivity

### 2015-05-13 draft.tex
fixed typo

We claim that the following ILP captures SSC exactly. 
SSC-LP:
\begin{align}
\min & \sum c(x) x_e  \\
\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{for each }S\text{ where } S_i \subset S,T_i \subset V - S, \\ & \hspace{1in}\delta(S) \text{ is the edges of the $S$ cut } \\
& x_e \in [0,1] \text{ for all }e \in E
\end{align}

@@

Of course, since this is an integer linear program, we must relax it to fractional solutions in order to solve it. Thus, we relax the constraint of $x_e \in [0,1]$ to $0 \leq x_e \leq 1$. However, there is still a slight issue; there can be exponentially many constraints. This is because there are exponentially many choices of $S$ for each $(S_i,T_i)$ pair. To get around this issue, we note that the ellipsoid algorithm can handle linear programs with arbitrarily many constraints, as long as it is given a separation oracle. Luckily, we can give such an oracle.

>>>>

We claim that the following ILP captures SSC exactly. 
SSC-LP:
\begin{align}
\min & \sum c(x) x_e  \\
\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{for each }S\text{ where } S_i \subset S,T_i \subset V - S, \\ & \hspace{1in}\delta(S) \text{ is the edges of the $S$ cut } \\
& x_e \in \{0,1\} \text{ for all }e \in E
\end{align}

@@

Of course, since this is an integer linear program, we must relax it to fractional solutions in order to solve it. Thus, we relax the constraint of $x_e \in \{0,1\}$ to $0 \leq x_e \leq 1$. However, there is still a slight issue; there can be exponentially many constraints. This is because there are exponentially many choices of $S$ for each $(S_i,T_i)$ pair. To get around this issue, we note that the ellipsoid algorithm can handle linear programs with arbitrarily many constraints, as long as it is given a separation oracle. Luckily, we can give such an oracle.
